---
title: "flowrpowr: packages and functions as skewed mandalas"
author: "L. Vaudor"
date: "6/09/2019"
output: html_document
---

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
set.seed(33)
```

```{r}
devtools::install_github("lvaudor/flowrpowr")
library(flowrpowr)
```

The convention for naming functions and functions' arguments of packages in the tidyverse is such that these function names and arguments names help understand their purpose and architecture.

The `flowrpowr` package exploits that characteristic to produce graphs which intend to facilitate the exploration and understanding of a package's content.

Let's explore, for instance, the `stringr` package:

```{r, fig.width=6, fig.height=6}
flowr_package("stringr")
```

This graph lets us understand that all functions in this package will start with prefix "str_" and then lists all possible combinations (all functions of type `str_*()`, for instance `str_c()` and `str_*_*()` -for instance `str_replace_all()` )

