---
title: "flowrpowr: graph representation of packages and functions"
author: "L. Vaudor"
date: "6/09/2019"
output: html_document
---

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
set.seed(33)
```

```{r}
#options(download.file.method = "libcurl")
#devtools::install_github("lvaudor/flowrpowr")
#devtools::install_github("thomasp85/ggforce")
library(flowrpowr)
```

The **convention for naming functions and functions' arguments** of packages in the tidyverse is such that these functions and arguments' names help understand their **purpose and construction**.

The `flowrpowr` package exploits that characteristic to produce **graphs which intend to facilitate the exploration and understanding of a package's content and of functions' arguments**.

## Package's functions

Let's explore, for instance, the `stringr` package:

```{r flowr_stringr, fig.width=8, fig.height=6}
flowr_package("stringr")
```

This graph lets us understand that many functions in this package will start with prefix "str_" and then lists all possible combinations (all functions of type `str_*()`, for instance `str_c()` and `str_*_*()` -for instance `str_replace_all()`-).

In the case of `stringr` the common root `str_`for many functions makes a tree-like layout easily readable:


```{r flowr_stringr_sugiyama, fig.width=8, fig.height=6}
flowr_package("stringr", layout="sugiyama")
```

Some packages gather many functions, which makes it preferable to display only some functions in the graph. For instance, the `ggraph` package is quite big to be displayed in a single graph:

```{r flowr_ggraph, fig.width=8, fig.height=6}
flowr_package("ggraph")
```

So it might be useful to display **only part of the graph** making use of an **element of interest**. For instance, if I'm looking, specifically, for some function regarding the edges, I can either highlight the elements linked to node "edge" (and thus still display all other elements)

```{r show_graph_highlighted, fig.width=8, fig.height=6}
flowr_package("ggraph", highlighted="edge")
```

or just keep the elements in the graph:

```{r flowr_ggraph_edge,fig.width=8, fig.height=6}
flowr_package("ggraph", element="edge")
```


# Functions' arguments

It is also possible to explore the **arguments to one or several functions**. Examining several functions at once help understand the arguments they have **in common** and the ones that are **specific** to each.

A few functions mean a few distinct roots, which might be well suited to a Sugiyama layout:

```{r flowr_functions, fig.width=8, fig.height=6}
flowr_function(c("geom_violin","geom_point","geom_boxplot"),
               layout="sugiyama")
```
